THESIS PROJECT PROPOSAL

### 2019-11-06 project_ashish/paper.tex
changes

\author[]{Ashish Sehrawat}
%\author[]{Director: Dr. Jose Feliciano Benitez Rubio}

@@

\address[mymainaddress]{Universidad de Sonora}
%\address[mysecondaryaddress]{360 Park Avenue South, New York}

%\begin{keyword}\rm
%\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
%The paper...
%\end{adjustwidth}
%\end{keyword}

@@

\section{BACKGROUND}
\cite{Dirac1953888}

-SM, Higgs, couplings, previous Higgs measurements, previous tH searches

SM, Higgs, couplings, previous Higgs measurements, previous tH searches\\

@@

Fermi$’$s treatment of beta decay 

@@

\section{GENERAL OBJECTIVE}
- motivation, tH production crossection, sign of k_t, search for BSM, ..

\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises 
only $5\%$ of the universe, another 
$25\%$ includes what we call dark matter. Understanding the production of the Higgs boson, as 
well as its decays like the invisible decay modes are an important part of the physics 
program of CERN laboratory experiments to verify the Standard Model and look for new 
particles. Through this project we will investigate the production of the Higgs boson in 
association with a single top quark (tH) in proton-proton collisions with the CMS experiment 
of the LHC. We will study the distribution of events in one of the decay channels and the 
sensitivity that we get with the current data. The main objective is to search for new 
processes such as tH Higgs production mode in the CMS experiment which require to study 
different aspects such as the model of the noises that are made by simulation, techniques of 
adjustments to the data that incorporate the different noises and the signal, and estimates 
of statistical and systematic uncertainties.
Some of the objectives in this project include:\\
\begin{itemize}
\item study one or more decay channels.\\
\item verify that simulation of signal events is adequate.\\
\item study the extraction of signal strength through adjustments to the data.\\
\item study the impact of statistical and systematic uncertainties.\\
\end{itemize}

%\section{SPECIFIC OBJECTIVES}
%- details

@@

\section{figures}

>>>>

\author[]{Ashish Sehrawat$^a$}
\author[]{Dr. Jose Feliciano Benitez Rubio$^b$}

@@

\address[mymainaddress]{Universidad de Sonora}
%\address[mysecondaryaddress]{Universidad de Sonora}

\begin{keyword}\rm
\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
Higgs boson, Higgs boson production, Higgs boson decay, Higgs boson coupling, 
\end{adjustwidth}
\end{keyword}

@@

\section{BACKGROUND}

-SM, Higgs, couplings, previous Higgs measurements, previous tH searches\\

@@

Fermi's treatment of beta decay 

@@

\section{GENERAL OBJECTIVE}
- motivation, tH production crossection, sign of $k_t$, search for BSM, ..

\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises 
only $5\%$ of the universe, another 
$27\%$ includes what we call dark matter. Understanding the production of the Higgs boson, as 
well as its decays like the invisible decay modes are an important part of the physics 
program of CERN laboratory experiments to verify the Standard Model and look for new 
particles. Through this project we will investigate the production of the Higgs boson in 
association with a single top quark (tH) in proton-proton collisions with the CMS experiment 
of the LHC. We will study the distribution of events in one of the decay channels and the 
sensitivity that we get with the current data. The main objective is to search for new 
processes such as tH Higgs production mode in the CMS experiment which require to study 
different aspects such as the model of the noises that are made by simulation, techniques of 
adjustments to the data that incorporate the different noises and the signal, and estimates 
of statistical and systematic uncertainties.
Some of the objectives in this project include:\\
\begin{itemize}
\item study one or more decay channels.\\
\item verify that simulation of signal events is adequate.\\
\item study the extraction of signal strength through adjustments to the data.\\
\item study the impact of statistical and systematic uncertainties.\\
\end{itemize}

\section{SPECIFIC OBJECTIVES}
- details

@@

\newpage
\cleanpage
